### 2014-08-15 paper/paper.Rmd
hides output

```{r load_packages, echo = FALSE, message = FALSE, warning = FALSE}
library(dplyr)
library(stringr)
```

```{r load_data, echo = FALSE, message = FALSE, warning = FALSE}
# This is the scaffolding to import the data
sets <- c("item", "parent", "school", "scoredItem", "student")

>>>>

```{r load_packages, echo = FALSE, message = FALSE, warning = FALSE, results='hide'}
library(dplyr)
library(stringr)
```

```{r load_data, echo = FALSE, message = FALSE, warning = FALSE, results='hide'}
# This is the scaffolding to import the data
sets <- c("item", "parent", "school", "scoredItem", "student")
